Responses to the Reviewers' Comments

### 2024-10-16 Response/Paper_Res.tex
Rev_V6.1

\textcolor{blue}{To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} hold promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives.
	While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
	QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.}

@@

\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.6}
		\captionsetup{name=TABLE}
		\caption{\textcolor{blue}{Comparison of Related Works \vspace{4mm}}}
		\scalebox{0.7}{%
			\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3.1cm}p{4.6cm}l} 
				\toprule
					\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
					\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a singel MEC system model  \\\midrule
					\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
					\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
					\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
					\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
					\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
					\cite{wu2023computation}  & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
					\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
					\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
					\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
					\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
					\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
					\cite{wu2024combining}  & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
					\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
					\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
					\cite{Bolourian-WCL24}  & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
					QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
					\toprule
			\end{tabular}}
			\label{table1}}
	\end{table*}

@@

	\item \textcolor{blue}{\textbf{DCDRL~\cite{qiu2020distributed}:} This method is a distributed optimization algorithm designed for delay-sensitive tasks in a queuing-based MEC environment, where MDs strategically interact with multiple ENs. We select DCDRL as a benchmark due to its similarity to our work. It is based on the actor-critic framework \cite{konda1999actor}, which underpins many state-of-the-art DRL algorithms, such as DDPG \cite{lillicrap2015continuous}, and PPO \cite{schulman2017proximal}}.

@@

	\item \textbf{Authors}:  $_*$Iman Rahmati, $_+$Hamed Shah-Mansouri, and $_*$Ali Movaghar

	Department of Computer Engineering, Sharif University of Technology, Tehran, Iran

	\item \textbf{Affiliation}: $_*$ Departments of Computer Engineering,  Sharif University of Technology, Tehran, Iran, $_+$ Department of Electrical Engineering, Sharif University of Technology, Tehran, Iran.

@@

\underline{Authors' Reply}: To address the reviewer comment, we have carefully studied the recently published papers and throughly revised the related work section. To be more specific,
\begin{itemize}
\item a) We have included the literature review in Section II of the revised manuscript and provided a survey of the recently published state-of-the-art works.
\item b) Furthemore, we have expanded the explanations about each related work and discussed their pros/vons.
\end{itemize}\vspace{6mm}
The newly added Section II of the revised manuscript is as follows. \newline
\begin{my}{1cm}{1cm}
	\rev{\setcounter{section}{1}
\section{Related Work}
\label{section:II}
\,\,\,\,In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.
		We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table111} provides an intuitive comparison of the related works.
	\subsection{DRL-based Computation Offloading for MEC}
	\,\,\,\,To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
	Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
	Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading. 
	These works in \cite{huang2019deep}, \cite{liu2021learn} do not account for delay-sensitive tasks and may overlook critical performance factors in real-time applications. Besides, these studies \cite{huang2019deep}--\cite{zhou2021deep} primarily investigate simplified MEC networks, focusing on single MEC network models, considering only single-server or single-user scenarios, which may not always reflect real-world scenarios. 
	Moreover, due to the absence of robust underlying resource scheduling systems, issues such as data congestion during transmission and resource allocation can arise, leading to suboptimal system performance. Therefore, more accurate MEC models are needed to address the complexities of dynamic resource scheduling in large-scale scenarios. \vspace{2mm}

@@

	\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.6}
		\captionsetup{name=TABLE}
		\caption{\textcolor{blue}{Comparison of Related Works \vspace{4mm}}}
		\scalebox{0.7}{%
			\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3.1cm}p{4.6cm}l} 
				\toprule
				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
				\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a singel MEC system model  \\\midrule
				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
				\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
				\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
				\cite{wu2023computation}  & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
				\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
				\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
				\cite{wu2024combining}  & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
				\cite{wu2023multi} 1& Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
				\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
				\cite{Bolourian-WCL24}  & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
				QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
				\toprule
		\end{tabular}}
		\label{table111}}
\end{table*}

@@

\textcolor{blue}{\,\,\,\,To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} hold promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives.
	While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
	QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.} \vspace{2mm}

@@

\underline{Authors' Reply}: To address the reviewer’s comment, we have further specified the contributions and highlighted the role of the LSTM network and its impact on the convergence and performance of the QECO algorithm. First, to further clarify our contributions, we have revised Section I as follows.

@@

\dots
}}
\end{my}
\vspace{5mm}

Second, we have extended the performance evaluation by comparing the performance of our proposed algorithm with vanilla DQN and DDQN \cite{van2016deep} to further specify the impacts of the LSTM network and dueling architecture. We have added Fig. 7 to Section V of the revised manuscript.
This figure highlights the positive effect of workload prediction by the LSTM network. This prediction contributes to improving the efficient utilization of the processing capabilities of ENs, leading to faster convergence of the QECO algorithm and achieving a higher average QoE compared to other methods.

@@

\underline{Authors' Reply}: (a) Task sizes are chosen from a discrete set because, in most applications, tasks have specific sizes. For instance, in image and video processing, tasks are typically divided into standardized sizes [X,XX,XXX]. Therefore, we assume that task sizes are selected randomly and uniformly from this discrete set. To address the reviewer’s comment and to provide further clarity regarding task sizes, we have revised the second paragraph of Section II as follows.

@@

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{blue}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), reflecting the standardized task sizes commonly used in practice, where \( \theta \) represents the number of these values.} Hence, $\lambda_i(t) \in \Lambda \cup \{0\}$ to consider the case that no task has arrived. We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.

@@

(b) To address the reviewer’s comment regarding the inclusion of the indicator function $y_{i,j}(t)$, we have revised Equations 16 and 17 in Section III, and Equations 21 and 22 in Section IV of the revised manuscript, as follows:
		\begin{my}{1cm}{1cm}
	\rev{
		{\
\begin{alignat}{1}
	E_i^{\text{I}}(t) = \textcolor{blue}{\sum_{\mathcal{J}} y_{i,j}(t)} D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, %= {\lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over \mathcal{B}_j(t) f_j^{\text{E}}} p_i^{\text{I}},
	\label{116}
\end{alignat}
\begin{alignat}{1}
	E_i^{\text{O}}(t) = E_i^{\text{T}}(t) + \sum_{\mathcal{J}} \textcolor{blue}{y_{i,j}(t)} E_{i,j}^{\text{E}}(t) + E_i^{\text{I}}(t).
	\label{17}
\end{alignat}
\setcounter{equation}{20}
	\hspace{-10mm}$\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
\begin{alignat}{1}
 \hspace{-10mm}(1-x_i(t))\Big(l_i^{\text{C}}(t) - t + 1\Big)  +  x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t'=t}^{T} \mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)} \, l_{i,j}^{\text{E}}(t') - t +1\bigg),
	\label{21}  
\end{alignat} 
\begin{alignat}{1}
	\hspace{-10mm}\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+  x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t^{'}=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)}  E_i^{\text{O}}(t)  \bigg).
	\label{22}  
\end{alignat}
}}
\end{my}

@@

Additionally, to address the reviewer's concern about merely introducing the results, we have revised the performance comparison Subsection in Section V, as bellow:

@@

(b) To address the reviewer’s comment, we have removed a few of outdated references and cited 13 recently published papers as follows. \newline

>>>>

\textcolor{blue}{To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives.
	While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
	QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.}

@@

\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.6}
		\captionsetup{name=TABLE}
		\caption{\textcolor{blue}{Comparison of Related Works \vspace{4mm}}}
		\scalebox{0.7}{%
			\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3.1cm}p{4.6cm}l} 
				\toprule
					\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
					\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a single MEC system model  \\\midrule
					\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a single MEC system model \\\midrule				
					\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
					\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
					\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
					\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
					\cite{wu2023computation}  & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
					\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
					\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
					\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
					\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
					\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
					\cite{wu2024combining}  & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
					\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
					\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
					\cite{Bolourian-WCL24}  & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
					QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
					\toprule
			\end{tabular}}
			\label{table1}}
	\end{table*}

@@

	\item \textcolor{blue}{\textbf{DCDRL~\cite{qiu2020distributed}:} This method is a distributed optimization algorithm designed for delay-sensitive tasks in a queuing-based MEC environment, where MDs strategically interact with multiple ENs. We select DCDRL as a benchmark due to its similarity to our work. It is based on the actor-critic framework \cite{NIPS1999_6449f44a}, which underpins many state-of-the-art DRL algorithms, such as DDPG \cite{lillicrap2015continuous}, and PPO \cite{schulman2017proximal}}.

@@

	\item \textbf{Authors}:  $^\ast$Iman Rahmati, $^\dagger$Hamed Shah-Mansouri, and $^\ast$Ali Movaghar

	\item \textbf{Affiliation}: $^\ast$ Department of Computer Engineering,  Sharif University of Technology, Tehran, Iran, \\ $^\dagger$ Department of Electrical Engineering, Sharif University of Technology, Tehran, Iran.

@@

\underline{Authors' Reply}: To address the reviewer comment, we have carefully studied the recently published papers and throughly revised the related work section. To be more specific,
\begin{enumerate}[]
\item We have devoted Section II of the revised manuscript to the literature review and provided a survey of the recently published state-of-the-art works.
\item Furthemore, we have expanded the explanations about each related work and discussed their pros/cons.
\end{enumerate}\vspace{6mm}
The newly added Section II of the revised manuscript is as follows. We have also included a table to provide a comprehensive comparison of the related works. \newline
\begin{my}{1cm}{1cm}
	\rev{\setcounter{section}{1}
\section{Related Work}
\label{section:II}
\,\,\,\,In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.
		We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table111} provides an intuitive comparison of the related works.
	\subsection{DRL-based Computation Offloading for MEC}
	\,\,\,\,To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
	Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
	Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading. 
	These works in \cite{huang2019deep}, \cite{liu2021learn} do not account for delay-sensitive tasks and may overlook critical performance factors in real-time applications. Besides, these studies \cite{huang2019deep}--\cite{zhou2021deep} primarily investigate simplified MEC networks, focusing on single MEC network models, considering only single-server or single-user scenarios, which may not always reflect real-world scenarios. 
	Moreover, due to the absence of robust underlying resource scheduling systems, issues such as data congestion during transmission and resource allocation can arise, leading to suboptimal system performance. Therefore, more accurate MEC models are needed to address the complexities of dynamic resource scheduling in large-scale scenarios. \vspace{2mm}

@@

	\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.6}
		\captionsetup{name=TABLE}
		\caption{\textcolor{blue}{Comparison of Related Works \vspace{4mm}}}
		\scalebox{0.7}{%
			\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3.1cm}p{4.6cm}l} 
				\toprule
				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
				\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a single MEC system model  \\\midrule
				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a single MEC system model \\\midrule				
				\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
				\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
				\cite{wu2023computation}  & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
				\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
				\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
				\cite{wu2024combining}  & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
				\cite{wu2023multi} 1& Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
				\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
				\cite{Bolourian-WCL24}  & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
				QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
				\toprule
		\end{tabular}}
		\label{table111}}
\end{table*}

@@

\textcolor{blue}{\,\,\,\,To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives.
	While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
	QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.} \vspace{2mm}

@@

\underline{Authors' Reply}: To address the reviewer’s comment, we have further explained how the proposed algorithm enhances the performance of the computation offloading in MEC and specified the contributions. We have also highlighted the role of the LSTM network and its impact on the convergence and performance of the QECO algorithm. First, to further clarify our contributions, we have revised Section I as follows.

@@

\end{itemize}
\dots
}}
\end{my}
\vspace{5mm}

Second, to highlight the impacts of the LSTM network and dueling architecture, we have extended the performance evaluation by comparing the performance of our proposed algorithm with vanilla DQN and DDQN \cite{van2016deep}. We have added Fig. 7 to Section VI of the revised manuscript.
This figure highlights the positive effect of workload prediction by the LSTM network. This prediction contributes to improving the efficient utilization of the processing resources of ENs, leading to faster convergence of the QECO algorithm and achieving a higher average QoE compared to other methods.

@@

\underline{Authors' Reply}: (a) Task sizes are chosen from a discrete set as most applications have tasks with predefined sizes. For instance, in image and video processing, tasks are typically divided into standardized sizes [X,XX,XXX]. Therefore, we assume that task sizes are selected randomly and uniformly from this discrete set. To address the reviewer’s comment and to provide further clarity regarding task sizes, we have revised the second paragraph of Section II as follows.

@@

\color{black}
We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{blue}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), where \( \theta \) represents the number of these values. Note that task sizes are drawn from a discrete set since, in many applications, tasks typically come with predefined sizes. We consider, $\lambda_i(t) \in \Lambda \cup \{0\}$ to include the case that no task has arrived.} We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.

@@

(b) We have considered the selected edge server and indecated offloaded task in previous version of manuscript, in Equations (16) and (17)

We need to explain whether it was correct before. Why we didn't have y before? You can say that we had considered the selected edge server before, but to make it more clear, we have included y to show the edge server selection.

To address the reviewer’s comment regarding the inclusion of the indicator function $y_{i,j}(t)$, we have revised Equations (16) and (17) in Section III, and Equations (21) and (22) in Section IV of the revised manuscript, as follows:
\setcounter{equation}{16}
		\begin{my}{1cm}{1cm}
	\rev{
		{\ \color{black}
%\begin{alignat}{1}
%	E_{i,j}^{\text{I}}(t) = \textcolor{blue}{\sum_{\mathcal{J}} y_{i,j}(t)} D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, %= {\lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over \mathcal{B}_j(t) f_j^{\text{E}}} p_i^{\text{I}},
%	\label{16}
%\end{alignat}
\begin{alignat}{1}
	E_i^{\text{O}}(t) = E_i^{\text{T}}(t) + \sum_{\mathcal{J}} \textcolor{blue}{y_{i,j}(t)} E_{i,j}^{\text{E}}(t) + E_i^{\text{I}}(t).
	\label{17}
\end{alignat}
\setcounter{equation}{20}
	\hspace{-10mm}$\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
\begin{alignat}{1}
 \hspace{-10mm}(1-x_i(t))\Big(l_i^{\text{C}}(t) - t + 1\Big)  +  x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t'=t}^{T} \mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)} \, l_{i,j}^{\text{E}}(t') - t +1\bigg),
	\label{21}  
\end{alignat} 
\begin{alignat}{1}
	\hspace{-10mm}\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+  x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t^{'}=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)}  E_i^{\text{O}}(t)  \bigg).
	\label{22}  
\end{alignat}
}}
\end{my}

@@

Additionally, to address the reviewer's concern about merely introducing the results, we have revised the performance comparison Subsection in Section VI, as bellow:

@@

(b) To address the reviewer’s comment, we have removed a few outdated references and cited 13 recently published papers as follows. \newline
